---
title: "Data Check"
author: "Patrick Harned"
date: "9/3/2019"
output: html_document
---

```{r setup, include=FALSE}
source("/Users/pharned/Google Drive/Coding/R Projects/Arab-Barometer-Wraps/Functions.R")
source("/Users/pharned/Documents/Arab-Barometer/Data Validation/Data Check.R")

abv=abv_en
knitr::opts_chunk$set(echo = FALSE)
```








Q211 Lebanon,Palestine if Q211=SYSMIS and Q210 in (1,2,3) -> 99. Libya dirty code 0->sysmis (filter). 

```{r}
variables = c("Q211", "Q210")
abv%>%
  filter(Q210 %in% c(1:3)&Q211%in%c(NA))%>%
  select(id, country,Q210, Q211)%>%
  print(n=100)
```
Palestine,Yemen: incorrect filter, some answers for q210=not at all, dk,refused
This means there are observations im Q210 (to what extent do you t hink that corruption is present) saying (dont know, no extent, or refused), but we see the same observations reporting that they belive the government is tackling corruption to a certain extent for Q211 (1/3)

```{r}
abv%>%
  filter(country %in%c(15,22))%>%
  filter(Q210%in%c(98,99, NA, 4), Q211%in%c(1:3))%>%
  select(country, id, Q211, Q210)%>%
  print(n=100)
```

Q211A Lebanon, Palestine if Q211A=sysmis and Q210 in (1,2,3) -> 99 Kuwait,Yemen no filtering. Palestine incorrect filter, some answers for q210=not at all, dk, refused

Q211A is extent of corruption at the local level. Interviewers were not supposed to ask this question ( but i think its kind of silly because its possibole that people think that the national government isnt corrupt but the local government is.)



```{r}
 abv%>%
  filter(Q210%in%c(1:3)&Q211A%in%c(NA))%>%
  select(country,splita, id, Q211A, Q210)%>%
  print(n=100)
 abv%>%
  filter(Q210%in%c(4,98,99,NA), Q211A%in%c(1:3))%>%
    select(country, id, splita, Q211A, Q210)%>%
  print(n=100)

```



Only Muslims were supposed to be asked q602_4a, bu there are about 80 observations from Lebanon where a non muslim was asked. All of those are Druze, and one Catholic.
```{r}
abv%>%
  filter_at(c("Q602_4A"), any_vars(.%nin%c(NA)))%>%
  filter(country%nin%c(9)&Q1012!=1)%>%
  select(country, id, splita, Q602_4A, Q1012, Q1012A)%>%
  print(n=100)
```




Yemen incorrect filter. some answers for splita=1
```{r}

abv%>%
  filter_at(c("Q604B_1", "Q604B_3"), any_vars(.%nin%c(NA)))%>%
  filter(country!=9&splita==1)%>%
  select(country, id, splita, Q604B_1,Q604B_3)%>%
  print(n=100)
```


Q605 Lebanon, Asked only to Muslim

Q605A_xxx,Q605B All countries, if Q605A_xxx=sysmis and splita=2-> 99 refused.

Actually only  relevant for Lebanon, Iraq and Libya


```{r}

abv %>% 
    filter_at(dplyr::vars(starts_with("Q605")), any_vars(. %in%c(NA)))%>%
  filter(country!=9&splita==2&Q1012==1)%>%
  select(id, country, starts_with("Q605A"))%>%
  print(n=100)
  


```
Yemen incorrect filter. some answers for splita=2
```{r}
abv %>% 
    filter_at(dplyr::vars(starts_with("Q605A")), any_vars(. %nin%c(NA)))%>%
  filter(country==22&splita==1&Q1012==1)%>%
  select(id, country, splita, starts_with("Q605A"))%>%
  print(n=100)
```



Q607_7 Lebanon, Asked only to Muslims - Question was also asked to Druze in Lebanon 


```{r}
abv%>%
  filter_at(dplyr::vars(starts_with("Q607")), any_vars(.%nin%c(NA)))%>%
  filter(Q1012!=1)%>%
  select(id, country, Q1012, Q1012A,starts_with("Q607"))%>%
  print(n=100)
```

Yemen incorrect filter, some answers for splita=1 ( again i think he means 2 here)

```{r}
abv%>%
  filter_at(c("Q703"), any_vars(.%nin%c(NA)))%>%
  filter(splita==2&country!=9)%>%
  select(id, country, Q703)%>%
  print(n=100)
```
 Yemen incorrect filter. some answers for Q851B=refused, dk or no or INAP ( not sure what this means)
```{r}

abv%>%
  filter(Q851B%nin%c(NA)&Q851A%in%c(2,98,99))%>%
  select(id, country, Q851B, Q851A)%>%
  print(n=100)

```
Q855A  Yemen, few incorrect answers for splita=1
Q855B Yemen, few incorrect answers for splita=1
Yemen incorrect filter, some answers for splita=1
```{r}
abv_en%>%
  filter_at(c("Q852","Q853A", "Q854", "Q855A", "Q855B"), any_vars(.%nin%c(NA)))%>%
              filter(splita==1&country!=9)%>%
  select(id, country, splita, Q852,Q853A,Q854,Q855A,Q855B)%>%
  print(n=100)
```


 Q853A Iraq, Filter, some female have answered. 
```{r}

```

These are all incorrect observations for splita=1/2
```{r}
map(fix_splits, print, n=1000)
```
Q853B Morocco if splita=2 and Q1002=1 and q853B=sysmis ->99 Refused.  Palestine: Filter only by splita=2. Yemen, only filter by split A=2 with few incorrect answers for splita=1

A1 Region not labelled for Kuwait and not available for Lebanon

A1 does not exist for Lebanon as we stratified by sect. We have no clear list for Kuwait, it might be worth setting it to . for Kuwait too. 


Q1001A Unlabelled governorate Sudan 190011 Set to "White Nile"

Already corrected. 


Q1001B: Iraq,Libya, Morocco, Palestine, Tunisia Revise codes 98,99... are they 998,999?

Could be valid code, the DK and REF codes are 998 and 999. This is about years living in the neighborhood. We have some old ages, so I would not drop 99 and 98. 

Iraq: code 100 recoded to 0
Sudan code 243 set to 0
Tunisia code 138 recoded to 0

I am not sure this is ok. Would recommend coding as .

Q1014A Algeria: Value 47 strange. Yemen: value 26 strange

Corrected in our latest file as 9 or more. 

Q1018: Lebanon: Sysmis assumed 0?

Yes, we only have 50 cases with member of HH with a disability, should be recoded

Q1015A_YEM Yemen has only values 0 or 1, unlabelled.

Already corrected. 

WT:
Libya Equilibrate =WT*0.9829659318637163, also there are 17 cases with very high weight
Palestine: Equilibrate: =WT*1.0071525732501436

Palestine cannot be changes as Walid weighted and we do not know how. Libya truncate, but mind you we will change the data book. 



