---
title: "Programming_Validation"
author: "Patrick Harned"
date: "9/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


source("/Users/pharned/Documents/Arab-Barometer/Wraps/Functions.R")
source("/Users/pharned/Documents/Arab-Barometer/Data Validation/Data_Recode(9:19).R")

library(kableExtra)
```

The following tables for questions that should only have been asked for Splita==2. 
I have filtered out all observations for Splita==1, which means that any remaining observations should only be NA.

## Q701C_5 and 6. 

If spita==2 - We have observations from Palestine and Yemen here. As you can see, there are a lot, probably PAPI, I dont think we can recode these. 
" Do you want foreign aid from
[COUNTRY] to increase, decrease, or remain the same in the future? "

```{r, Q701C_5}
kable(List2[["Q701C_5"]])

kable(List2[["Q701C_6"]])
```

## Q1017 if splita ==2. 

We have observations  from splita ==1 here in Yemen

Does your family receive
remittances from someone living abroad? 

```{r, Q1017}
kable(List2[["Q1017"]])
```

## Q605b. 
[PROGRAMMER: IF COUNTRY != 9 AND SPLITA == 2 & Q1012 == 1] Which of
these four aspects do you think the most essential aspect of shari’a government? 
```{r, Q605B}
kable(List2[["Q605B"]])
```

## Q601_9A: 

[PROGRAMMER: IF COUNTRY != 9 & SPLITA == 2]
Women’s inheritance should be equal to that of men.

```{r, Q601_9A}

kable(List2[["Q601_9A"]])
```
## Q853b. 

[PROGRAMMER: IF COUNTRY != 9 AND SPLIT A == 2 & Q1002 == 2] How
important do you think it is for a man to live up to an ideal of the female body as presented by the
media? 

```{r, Q853B}
kable(List2[["Q853B"]])
```
 
## Q853a.

[PROGRAMMER: IF COUNTRY != 9 AND SPLIT A == 2 & Q1002 == 1] How
important do you think it is for a man to live up to an ideal of the male body as presented by the
media?
```{r, Q853A}
kable(List2[["Q853A"]])
```

## Q201C

[PROGRAMMER: SEE SPECIFIC ITEMS] And how much trust do you have in… 

[PROGRAMMER: IF SPLIT A == 2;
ID COUNTRY != 9; ALL]

```{r, Q201C_40}
kable(List2[["Q201C_40"]])

kable(List2[["Q201C_32"]])

kable(List2[["Q201C_39"]])

kable(List2[["Q201C_38"]])
```

## Q604b_3. 

[PROGRAMMER: SEE SPECIFIC ITEMS] To what degree would each of the
following factors be an obstacle to accepting the marriage of a close male relative?

[PROGRAMMER: IF COUNTRY != 9 &
SPLITA == 1]
One who comes from a family with a lower
social status

```{r, Q604B_3}
kable(List1[["Q604B_3"]])
```

## Q204c. 

[PROGRAMMER: SEE SPECIFIC ITEMS] And how would you evaluate the current
government’s performance on [INSERT ITEM]? 
[PROGRAMMER: IF SPLITA==1 &
COUNTRY != 1 OR 9]

```{r, Q204C_15}
kable(List1[["Q204C_15"]])
kable(List1[["Q204C_13"]])
```



